replication_report

### 2015-04-03 replication_report.Rmd
added new table code

#compare models
anova(m1.cent, m2.cent)

#Work on tables:
#In another working document (because incomplete)
```

Graph results of moderation analysis

```{r, echo=FALSE}
##Scatterplots for add on to study graphs 
graph.simple = ggplot(dat, aes(x = , y = )) 
graph.simple + geom_smooth(method = "") +
  geom_point() +
  ggtitle("") +
  ylab("") +
  xlab("")

>>>>

#compare models
anova(m1.cent, m2.cent)
```

```{r, echo=FALSE}
#Work on tables:
##Basic Table to show frequencies
LikedMusic<- c("21(57%)","16(43%)", "")
DislikedMusic<- c("8(23%)","27(77%)", "N= 72, χ²(1)= 8.59, p= .003,Φ=.35")
Condition<- c("AdvertisedPen", "NonAdvertisedPen", "")
dfFreq=cbind(Condition, LikedMusic, DislikedMusic)

# Graph results of moderation analysis

##Scatterplots for add on to study graphs 
graph.simple = ggplot(dat, aes(x = , y = )) 
graph.simple + geom_smooth(method = "") +
  geom_point() +
  ggtitle("") +
  ylab("") +
  xlab("")
